\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-4pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-4pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\eduSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.9\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape Akash Jaiswal} \\ \vspace{4pt}
    \small \href{mailto:akashjaiswal3846@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{akashjaiswal3846@gmail.com}} ~ 
    \href{https://linkedin.com/in/akashjaiswal03}{\raisebox{-0.2\height}\faLinkedin\ \underline{/akashjaiswal03}}  ~
    \href{https://github.com/jaiakash}{\raisebox{-0.2\height}\faGithub\ \underline{/jaiakash}} ~
    \href{https://twitter.com/a_kashhhhhh_}{\raisebox{-0.2\height}\faTwitter\ \underline{/akashhhhhh}}
    \vspace{-8pt}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
      {\href{https://drive.google.com/file/d/108neUmfJqgKASZ2P7VFuHIYA8RGoLkk_/view?usp=drive_link}{Oracle India Pvt Ltd}}{May 2023 -- July 2023}
      {Project Intern}{Hyderabad, Telangana}
      \resumeItemListStart
        \resumeItem{Worked in FRE team, where we ideated, developed and deployed a full-stack application for auditing code violations and exceptions. The result saved 80$\%$ of FA developers and TA teams time spent over auditing code violations.}
        \resumeItem{Automated the full workflow in clean GUI instead of previously manual workflow involving complex Excel sheets.}
        \resumeItem{Tech stack - ReactJS, SpringBoot and Oracle DB. Improved collaboration, team work and communication skills while working in corporate environment.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://summerofcode.withgoogle.com/programs/2022/projects/Sg34Qe09}{CC Extractor (Google Summer of Code)}}{June 2022 -- Oct 2022}
      {Google Summer of Code 2022 Contributor}{Remote}
      \resumeItemListStart
        \resumeItem{Developed an app that lets the caller decide if the call is urgent or not to show the urgency of that call.}
        \resumeItem{I got unique opportunity to ideate and code from scratch. Got mentored from lead devs of org regarding tech, product design and helped other people in community while on boarding.}
        \resumeItem{Tech Stack -  Flutter, Figma and Firebase}
    \resumeItemListEnd

  \resumeSubheading
      {Connectezy}{Aug 2023 -- Present}
      {Software Developer}{Tiruchirappalli, Tamil Nadu}
      \resumeItemListStart
        \resumeItem{Worked on Connectezy, a startup focused on connecting people, especially alumni, responsible for product design, leading other developers and coordinating with other co-founder.}
        \resumeItem{Lead the product team in developing various features like hub, my network, chat and login, etc for the app. We also onboarded 800+ students from 2 different colleges.}
        \resumeItem{Tech Stack -  ReactJS, Figma and NodeJS}
    \resumeItemListEnd

    \resumeSubheading
      {\href{https://nitt.edu/home/students/clubsnassocs/techclubs}{Technical Council, NIT Trichy}}{May 2023 -- Present}
      {Technical Secretary}{Tiruchirappalli, Tamil Nadu}
      \resumeItemListStart
        \resumeItem{Selected as Technical Secretary 2023 - 2024, NIT Trichy, responsible for monitoring and managing the 17 technical clubs, Pragyan fest and overseeing various campus development initiatives at NIT Trichy.}
        \resumeItem{I also coordinate with the Centre of Excellence, ISRO incubation centre, Centre for Entrepreneurship Development and Incubation and other labs to ensure a thriving platform for the  students of NIT Trichy.}
        \resumeItem{Connducted TransfiNITTe, the annual flagship hackathon of NIT Trichy, with 50+ teams and 5 lakhs+ prizes pool.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
    \resumeItemListStart
        \resumeItem{Working on startup \textbf{Connectezy} which aims to connect alumni and students for collaboration, overseeing its development both from product and tech side.}
        \resumeItem{Chief community lead and CTO for Befikra Community, to help students with their careers, which has \textbf{3000+ members} around India.}
        \resumeItem{Speaker at \textbf{Twitter Space} session on "Open Source in Web2.0, Web3.0, and Metaverse" by GSSOC}
        \resumeItem{Speaker at \textbf{GDSC NIT Silchar} and \textbf{GDSC NIT Trichy} session on "Git it Done", attended by \textbf{200+ participants}.}
        \resumeItem{Lead open source community, TeCOS, NIT Trichy, where I helped students to get started in open source. \textbf{200+ students joined for events and 500+ member community}.}
        \resumeItem{Got a fully funded scholarship by \textbf{IIIT Hyderabad} and \textbf{Wikimedia Foundation} to attend 2nd Wikimedia Summit.}
        
    \resumeItemListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Javascript, C++, Python, Kotlin, C, Dart, C\# } \\
     \textbf{Tools}{: Git/Github, Figma, Google Cloud, AWS, CI/CD,  Docker,  Custom ROMs/Rooting} \\
     \textbf{Technologies}{: ReactJS/NextJS, Flutter, NodeJS, Android Dev, Web Dev, Unity3D, Firebase } \\
    }}
 \end{itemize}
 \vspace{-20pt}

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=10pt]
                \item Data Structures and Algorithms
                \item Software Project Management
                \item Operating Systems
                \item Web Technology
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
%\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology, Tiruchirappalli}{Nov 2020 - June 2024}
      {Bachelor of Technology, Civil Engineering (minor in Computer Science), 7.8/10}{Tiruchirappalli, Tamil Nadu}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \eduSubheading
      {St. Xavier\textquotesingle{}s School, Ramnagar}{Class 12th, CBSE, 91\%, May, 2020}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \eduSubheading
      {St. Peter\textquotesingle{}s School, Akbarpur}{Class 10th, ICSE, 91\%, May, 2018}
  \resumeSubHeadingListEnd


\end{document}
