\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-4pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-4pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\eduSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.9\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape Akash Jaiswal} \\ \vspace{4pt}
    \small \href{mailto:akashjaiswal3846@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{akashjaiswal3846@gmail.com}} ~ 
    \href{https://linkedin.com/in/akashjaiswal03}{\raisebox{-0.2\height}\faLinkedin\ \underline{/akashjaiswal03}}  ~
    \href{https://github.com/jaiakash}{\raisebox{-0.2\height}\faGithub\ \underline{/jaiakash}} ~
    \href{https://twitter.com/a_kashhhhhh_}{\raisebox{-0.2\height}\faTwitter\ \underline{/akashhhhhh}}
    \vspace{-8pt}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
      {\href{https://dharmikapp.in/}{Dharmik Website}}{Aug 2023 -- Nov 2023}
      {Software Developer}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Led the development of the Dharmik Website from concept to completion, creating a fully functional full-stack website in React.}
        \resumeItem{Implemented key features including responsive website, payment gateway with Razorpay, dynamic content translation, and authentication system.}
        \resumeItem{Utilized a tech stack of ReactJS for frontend development, Figma for design, and Firebase for backend services.}
    \resumeItemListEnd

  \resumeSubheading
      {\href{https://drive.google.com/file/d/108neUmfJqgKASZ2P7VFuHIYA8RGoLkk_/view?usp=drive_link}{Oracle India Pvt Ltd}}{May 2023 -- July 2023}
      {Software Developer Intern}{Hyderabad, Telangana}
      \resumeItemListStart
        \resumeItem{Contributed to the FRE team by designing, developing, and deploying a full-stack application for auditing code violations and exceptions, which reduced the time spent by FA developers and TA teams by 80\%.}
        \resumeItem{Streamlined and automated the auditing workflow through a clean GUI, replacing the previous manual process that relied on complex Excel sheets.}
        \resumeItem{Worked with a tech stack including ReactJS, SpringBoot, and Oracle DB, and for soft skills enhanced collaborative and communication skills while adapting to a professional corporate environment.}
      \resumeItemListEnd


    \resumeSubheading
      {\href{https://summerofcode.withgoogle.com/programs/2022/projects/Sg34Qe09}{CC Extractor (Google Summer of Code)}}{June 2022 -- Oct 2022}
      {Google Summer of Code 2022 Contributor}{Remote}
      \resumeItemListStart
        \resumeItem{Designed and developed an application that enables users to assess and indicate the urgency of incoming calls, enhancing call management and prioritization.}
        \resumeItem{Gained valuable experience by ideating and coding the project from the ground up, receiving mentorship from senior developers on technology, product design, and community support.}
        \resumeItem{Utilized Flutter for app development, Figma for design, and Firebase for backend services, contributing to both technical development and community onboarding.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}


\section{Open Source Contributions and Leadership}
    \resumeItemListStart
    % Condensed Open Source Contributions
    \resumeItem{
        \textbf{Processing}: \href{https://github.com/processing/p5.js/pull/6950}{PR #6950}, \href{https://github.com/processing/p5.js-website/pull/101}{PR #101}, \href{https://github.com/processing/p5.js/pull/6892}{PR #6892}, \href{https://github.com/processing/p5.js-website/pull/328}{PR #328}
        \item \textbf{Oppia}: \href{https://github.com/oppia/oppia/pull/19512}{PR #19512}, \href{https://github.com/oppia/oppia-web-developer-docs/pull/244}{PR #244}
        \textbf{Google Season of Docs}: \href{https://github.com/google/season-of-docs/pull/606}{PR #606}
        \item \textbf{Other Notable Contributions}:
            \href{https://github.com/sinha-debojyoti/Ookla-Speedtest.net-Crawler/pull/104}{Ookla-Speedtest.net-Crawler PR #104}, \href{https://github.com/wiredhikari/tuxfetch/pull/5}{Tuxfetch PR #5}, \href{https://github.com/crxjs/chrome-extension-tools/pull/675}{Chrome Extension Tools PR #675}, \href{https://github.com/OpenLake/Leaderboard-Pro/pull/105}{Leaderboard-Pro PR #105}, \href{https://github.com/anubhavpulkit/Open-Source-Events/pull/43}{Open-Source-Events PR #43}
        
    }
    \resumeItem{Led the \textbf{TeCOS} open source community at NIT Trichy, growing from 200+ to over 1000 members.}
    \resumeItem{Awarded a fully funded scholarship by \textbf{IIIT Hyderabad} and \textbf{Wikimedia Foundation} to attend the 2nd Wikimedia Summit.}
    \resumeItem{Delivered a keynote at \textbf{Twitter Space} on "Open Source in Web2.0, Web3.0, and Metaverse" organized by GSSOC.}
    \resumeItem{Presented at \textbf{GDSC NIT Silchar} and \textbf{GDSC NIT Trichy} on "Git it Done," with over 200 participants.}
    \resumeItem{Served as Technical Secretary 2023-2024 at NIT Trichy, managing 17 technical clubs and organizing \textbf{TransfiNITTe}, an annual hackathon at NIT Trichy, featuring 50+ teams and a prize pool of over 5 lakhs.}
    \resumeItem{Chief Community Lead for \textbf{Befikra Community}, which supports 3000+ members across India in career development.}
\resumeItemListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Javascript, C++, Python, Dart, C\# } \\
     \textbf{Tools}{: Git/Github, CI/CD,  Docker, Kubernetes, AWS, Google Cloud, Custom ROMs/Rooting} \\
     \textbf{Technologies}{: ReactJS/NextJS, Flutter, NodeJS, Android Dev, Unity3D, Firebase } \\
    }}
 \end{itemize}
 \vspace{-20pt}

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=10pt]
                \item Data Structures and Algorithms
                \item Software Project Management
                \item Operating Systems
                \item Web Technology
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
%\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology, Tiruchirappalli}{Nov 2020 - June 2024}
      {Bachelor of Technology, Civil Engineering (minor in Computer Science), 7.8/10}{Tiruchirappalli, Tamil Nadu}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \eduSubheading
      {St. Xavier\textquotesingle{}s School, Ramnagar}{Class 12th, CBSE, 91\%, May, 2020}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \eduSubheading
      {St. Peter\textquotesingle{}s School, Akbarpur}{Class 10th, ICSE, 91\%, May, 2018}
  \resumeSubHeadingListEnd


\end{document}
