\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-4pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-4pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\eduSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.9\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape Akash Jaiswal} \\ \vspace{4pt}
    \small \href{mailto:akashjaiswal3846@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{akashjaiswal3846@gmail.com}} ~ 
    \href{https://linkedin.com/in/akashjaiswal03}{\raisebox{-0.2\height}\faLinkedin\ \underline{/akashjaiswal03}}  ~
    \href{https://github.com/jaiakash}{\raisebox{-0.2\height}\faGithub\ \underline{/jaiakash}}
    \href{https://twitter.com/a_kashhhhhh_}{\raisebox{-0.2\height}\faTwitter\ \underline{/akashhhhhh}}
    \vspace{-8pt}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Oracle India Pvt Ltd}{May 2023 -- July 2023}
      {Project Intern}{Hyderabad, Telangana}
      \resumeItemListStart
        \resumeItem{Worked in FRE team, where we brainstormed, developed and deployed a full-stack application for managing exceptions and code violations and automated bug creation..}
        \resumeItem{Automated the full workflow and in clean, elegant UI instead of previously complex Excel sheets, saving 80$\%$ of FA developers and TA teams time spent over auditing code violations.}
        \resumeItem{Tech Stack - OJET, SpringBoot, Oracle DB}
      \resumeItemListEnd

    \resumeSubheading
      {CC Extractor (Google Summer of Code)\href{https://summerofcode.withgoogle.com/programs/2022/projects/Sg34Qe09}}{June 2022 -- Oct 2022}
      {Goggle Summer of Code 2022 Contributor}{Remote}
      \resumeItemListStart
        \resumeItem{Developed an app that lets the caller decide if the call is urgent or not. It enables the user to determine that the specific call is critical and that the person should be disrupted from whatever they might be doing.}
        \resumeItem{This project was from scratch and i got unique opportunity to ideate the product as well as code. Got mentored from lead devs of org regarding tech, product design and helped other people in community while onboarding.}
        \resumeItem{Tech Stack -  Flutter and Firebase}
    \resumeItemListEnd

    \resumeSubheading
      {Connectezy}{Aug 2023 -- Oct 2023}
      {Software Developer}{Tiruchirappalli, Tamil Nadu}
      \resumeItemListStart
        \resumeItem{Worked as lead software developer for Connectezy, a startup focused on connecting people, especially alumni, resposible for product design, leading other developers and working in close association with founder.}
        \resumeItem{Lead the tech team, developed various features like hub, my network, chat and login, etc for the app.}
        \resumeItem{Tech Stack -  Flutter, Figma, MongoDB and  NodeJS}
    \resumeItemListEnd

    \resumeSubheading
      {Technical Council, NIT Trichy}{May 2023 -- Present}
      {Technical Secretary}{Tiruchirappalli, Tamil Nadu}
      \resumeItemListStart
        \resumeItem{Selected as Technical Secretary 2023 - 2024, NIT Trichy, responsible for monitoring and managing the 17 technical clubs, Pragyan fest and overseeing various campus development initiatives at NIT Trichy.}
        \resumeItem{I also coordinate with the Centre of Excellence, ISRO incubation centre, Centre for Entrepreneurship Development and Incubation and other labs to ensure a thriving platform for the  students of NIT Trichy.}
        \resumeItem{Connducted TransfiNITTe, the annual flagship hackathon of NIT Trichy, with 50+ teams and 5 lakhs+ prizes pool.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
    \resumeItemListStart
        \resumeItem{Working on startup \textbf{Connectezy} which aims to connect alumni and students for collaboration, overseeing its development both from product and tech side.}
        \resumeItem{Chief community lead and CTO for \textbf{Befikra Community}, to help students with their careers, which has 3000+ members around India.}
        \resumeItem{Speaker at \textbf{Twitter Space} session on "Open Source in Web2.0, Web3.0, and Metaverse" by \textbf{GSSOC}}
        \resumeItem{Speaker at \textbf{GDSC NIT Silchar and GDSC NIT Trichy} session on "Git it Done", attended by 200+ participants.}
        \resumeItem{Lead \textbf{open source community}, \textbf{TeCOS, NIT Trichy}, where I helped students to get started in open source. 200+ students joined for events and 500+ member community.}
        \resumeItem{Got a fully funded scholarship by \textbf{IIIT Hyderabad} and \textbf{Wikimedia Foundation} to attend 2nd Wikimedia Summit.}
        
    \resumeItemListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Javascript, C++, Python, Kotlin, C, Dart, C\# } \\
     \textbf{Tools}{: Git/Github, Figma, Google Cloud, AWS, CI/CD,  Docker,  Custom ROMs/Rooting} \\
     \textbf{Technologies}{: ReactJS/NextJS, Flutter, NodeJS, Android Dev, Web Dev, Unity3D, Firebase } \\
    }}
 \end{itemize}
 \vspace{-20pt}

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=10pt]
                \item Data Structures and Algorithms
                \item Software Project Management
                \item Operating Systems
                \item Web Technology
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
%\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology, Tiruchirappalli}{Nov 2020 - May 2024 (Expected)}
      {Bachelor of Technology, Civil Engineering with minor in Computer Science, 7.8/10}{Tiruchirappalli, Tamil Nadu}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \eduSubheading
      {St. Xavier\textquotesingle{}s School, Ramnagar}{Class 12th, CBSE, 91\%, May, 2020}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \eduSubheading
      {St. Peter\textquotesingle{}s School, Akbarpur}{Class 10th, ICSE, 91\%, May, 2018}
  \resumeSubHeadingListEnd


\end{document}
