\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

\namesection{Akash}{Jaiswal}{akashjaiswal3846@gmail.com | Github \href{https://github.com/jaiakash}{\bf jaiakash} | LinkedIn \href{https://www.linkedin.com/in/akashjaiswal03}{\bf akashjaiswal03} | Bento.me \href{https://bento.me/akashjaiswal}{\bf akashjaiswal}} 

\begin{minipage}[t]{0.3\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{NIT TIRUCHIRAPALLI}
\descript{Btech - Civil (Minor in CSE)}
\location{2020 - 2024 (expected) | 8.01/10 }
\sectionsep

\subsection{St. Xavier\textquotesingle{}s School}
\descript{CBSE Std XII | 2020 | 91\% }
\sectionsep

\subsection{St. Peter\textquotesingle{}s School}
\descript{ICSE Std X | 2018 | 91\%}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github \href{https://github.com/jaiakash}{\bf jaiakash} \\
LinkedIn  \href{https://www.linkedin.com/in/akashjaiswal03}{\bf akashjaiswal03} \\
Twitter  \href{https://twitter.com/a_kashhhhhh_}{\bf akashhhhhh} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Clubs
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Clubs/Societies}

\subsection{Technical Council NITT}
\descript{Technical Secretary}
\location{Council for managing all techno-managerial affairs in NIT-T}
\sectionsep

\subsection{Delta Force NITT}
\descript{App Dev \textbar{} Full stack web dev}
\location{Official Web Team and programming club of NIT Trichy}
\sectionsep

\subsection{NITT Student Alumni Cell}
\descript{Manager}
\location{The Students Alumni Cell of NIT Trichy}
\sectionsep

\subsection{Athenæum - NIT Trichy}
\descript{Delegation}
\location{Official Model United Nations Society of NIT Trichy.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\subsection{Programming}
Java  \textbullet{} Javascript C++ \textbullet{} Python  \\
Kotlin \textbullet{} C \textbullet{} Dart \textbullet{} C\# \\ 
\sectionsep

\subsection{Tech Stacks}
Android Dev (Native) \textbullet{}   Web Dev  ReactJS/NextJS  \textbullet{} Flutter  \textbullet{} NodeJS Unity3D \textbullet{} Firebase 
\sectionsep

\subsection{Tools}
Git/Github  \textbullet{} Docker \textbullet{} Linux \textbullet{} CI/CD
\textbullet{} Shell/Bash \textbullet{} Azure \textbullet{} MongoDB \textbullet{}
Custom ROMs/Rooting \\ 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.69\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Experience
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\runsubsection{Google Summer of Code 2022}\descript{| \href{https://summerofcode.withgoogle.com/programs/2022/projects/Sg34Qe09}{\bf Contributor at CC Extractor}}\hfill \location{ June 2022 – Oct 2022 }
\begin{tightemize}
    \item Selected as contributor for GSoC'22 under CCExtractor.
    \item An app that lets the caller decide if the call is urgent or not. It enables the user to determine that the specific call is critical and that the person should be disrupted from whatever they might be doing.
    \item Tech stack is Flutter and Firebase.
\end{tightemize}
\sectionsep

\runsubsection{Nyayaag Advocate Website}\descript{| Internship | Software Developer}\hfill \location{ April 2022 – June 2022 }
\begin{tightemize}
    \item Worked as web developer for Nyayaag Advocate startup, incubated under CEDI NIT Trichy.
    \item Designed the website with features like user registration, login, and dashboard pages for advocates and clients
    \item Tech stack – Flutter, MongoDB and NodeJS
\end{tightemize}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Projects
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}
\raggedright

\runsubsection{\large{Code Character Web 2022}}
\descript{| ReactJS | Kotlin | Typescript }\hfill \href{https://github.com/delta/codecharacter-web-2022}{Github}\\
\begin{tightemize}
    \item A turn-based strategy game in which the player controls troops controls their troops by writing code in either of three languages: Java, C++ and Python while safeguarding their home-base from enemy attack.
    \item   The contest was live for 10 days with 250+ participants from 106 colleges and 20,000+ match simulations. 
    \item Developed – leader board and battle TV pages for code character web.
\end{tightemize}
\sectionsep

\runsubsection{\large{Delta Winter Of Code website}}
\descript{|  ReactJS | GraphQL | Javascript}\hfill \href{http://dwoc.io}{Website}\\
\begin{tightemize}
    \item Delta Winter of Code is an open-source program operated by Delta Force, NIT Trichy, to introduce programmers to open-source software.
    \item Developed the front end of the website, specifically the admin page.
    \item  I also participated as a mentor for Entrix organisation in DWoC 2021.
\end{tightemize}
\sectionsep

\runsubsection{\large{Sarkari Result ALL}}
\descript{| Java | Android studio | Google Analytics }\hfill \href{https://play.google.com/store/apps/details?id=com.amostrone.akash.sanjeevwebsolutions}{Play Store link}\\
\begin{tightemize}
    \item An android app that gives information about the availability of government job openings.
    \item The app provides a one-to-go solution for users who previously had to go to different websites. Improved user experience.
    \item   Used Google Analytics and Google Ad mob. 1k+ downloads on Play store.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Awards
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements/Open Source Contributions}
\runsubsection{\small{1st Prize in IIT Roorkee Cogni 2022 Cryptotrader}}

\runsubsection{\small{2nd Prize in NIT ConclaveX 2022 - Covalent (Technical Bounty)}}

\runsubsection{\small{Completed Kharagpur Winter Of Code 2021 by IIT KGP }}\href{https://kossiitkgp.org/public-files/KWoC/2021-Certificates/Student/jaiakash.pdf
}{Certificate Link}

\runsubsection{\small{Completed Hacktoberfest 2021 with 10+ projects }}

\runsubsection{\small{Codechef Global Rank 194 : INTERNATIONAL CODING MARATHON IIT BHU 2021}}\

\runsubsection{\small{3rd position in ICY Cup Spider - R\&D club of NIT Trichy | 2021}}\

\runsubsection{\small{3rd position in Code Connoisseurs Spider - R\&D club of NIT Trichy | 2021}}\

\sectionsep
\end{minipage} 
\ 
\end{document}
